INTELLIGENT SYSTEMS

### 2021-04-10 paper_6.tex
finish 6.3.3

>>>>

\subsection{THE PROPOSED APPROACH}
\subsubsection{Overview}
The work performed by the model is divided into three steps: \emph{coarse mask 
generation}, \emph{coarse mask enhancement}, and \emph{Recursive mask refinement} (Fig. \ref{fig:step}). In 
order to generate the initial masks, a CNN is trained and subsequently these 
are improved with a graph-based model. Images, enhanced masks and lables 
are used to train the model.
\begin{figure}[h!]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper6/step.png}
    \centering
    \caption{Steps of the proposed method.}
    \label{fig:step}
\end{figure}

\subsubsection{Coarse Mask Generation}
The generation of a mask must occur without any information on the labels.
The CNN present in \cite{0876055520} is used for this purpose. This network is trained 
with millions of unlabeled images and is also the fastest of other methods 
existing in the state of the art. Unfortunately, as seen in image \ref{fig:semanticWork}, the 
generated coarse masks appear to be inaccurate and do not correspond with 
the position of the underlying object.

\subsubsection{Coarse Mask Enhancement}
The enhancement of the mask is done before the net training process takes 
place. To carry out the improvement, the unsupervised GrubCut model \cite{0876055542} 
is used. This method performs segmentations that divide the background 
from the foreground using a Gaussian Mixture model to estimate the color 
distribution of objects. These distributions are used to construct a Markov 
Random Field on the labels of each pixel. A graph cut optimization has the 
task of maximizing the search for connected regions having the same label. 
There are two steps to apply the GrabCut:
\begin{enumerate}
    \item search for the smallest bounding box inside the mask.
    \item enhance the mask based on the previously created bounding box and on the RGB image.
\end{enumerate}
The enhanced mask will be used to recursively train the network.
